I can see clearly now: reinterpreting statistical significance

### 2018-11-05 doc.tex
MEE format

\flushbottom
\maketitle
\newpage
\thispagestyle{empty}

\clearpage

\linenumbers
\doublespacing

@@

\noindent Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation. We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''. Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g. whether we can clearly see that a correlation or between-group difference is positive or negative). We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''. This simple semantic change could substantially enhance clarity in statistical communication.

@@

\clearpage

@@

>>>>

\flushbottom
\maketitle
%\newpage
%\thispagestyle{empty}

%\clearpage

\linenumbers

\subsection*{Running Title}

Statistical Clarity

\subsection*{Word Count}

2,220

@@

\begin{enumerate}

\item Null hypothesis significance testing (NHST) remains popular despite decades of concern about misuse and misinterpretation. Recent suggestions for mitigating the problems of NHST that continue to plague ecology (and other fields) include calls for abandoning NHST in favor of Bayesian of information-theoretic approaches. Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g. whether we can clearly see that a correlation or between-group difference is positive or negative). 
\item We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''. We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''. We illustrate our point by rewriting common misinterpretations of the meaning of statistical tests found in the literature using the language of ``clarity''.
\item The meaning of statistical tests become easier to interpret and explain when viewed through the lens of ``statistical clarity''.
\item Our suggestion is mild, but practical: this simple semantic change could substantially enhance clarity in statistical communication.

\end{enumerate}

@@

\clearpage
\doublespacing

@@

%\clearpage
%\input{table.tex}
%\clearpage
